Challenges to transboundary fisheries management in North America under climate change

### 2020-04-29 Ecol/Manuscript_Draft.Rmd
Update paths

# source("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Functions/DBEM_imp_F.R") #Imports a single species

my_ggtheme_p() <- function() {
 theme(
  plot.title = element_text(size = rel(1), hjust = 0, face = "bold"),
  panel.background = element_blank(),
  strip.background = element_blank(),
  # strip.text    = element_text(size = base_size, face = "italic"),
  panel.border   = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  axis.ticks = element_blank(),
  axis.text.x = element_text(size = 14,
                angle = 0,
                face = "plain"),
  axis.text.y = element_text(size = 14),
  axis.title = element_text(size = 14),
  legend.key = element_rect(colour = NA, fill = NA),
  legend.position = "top",
  legend.title = element_text(size = 16),
  legend.text = element_text(size = 14),
  strip.text.x = element_text(size = 10, colour = "black"),
  strip.text = element_text(size = 18)
 )
}

my_ggtheme_m() <- function(base_size = 9, Region = "NA") {

 theme(text       = element_text(#family = "Helvetica",
  color = "gray30", size = base_size),
  plot.title    = element_text(size = rel(1.25), hjust = 0, face = "bold"),
  panel.background = element_blank(),
  panel.border   = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_line(color = "transparent"),
  strip.background =element_rect(fill = "transparent"),
  strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
  axis.line    = element_blank(), # element_line(colour = "grey30", size = .5))
  axis.ticks    = element_blank(),
  axis.text    = element_blank(),
  axis.title    = element_blank(),
  # legend.key    = element_rect(colour = NA, fill = NA, size = 4),
  legend.position = "bottom"#,
  # legend.key.width =unit(6,"line")
 )
}

@@

# End Century
End_In <- paste(2080);End_In # 2090
End_End <- paste(2099);End_End

Data_Path <- "~/Documents/UBC/OC_Special_Issue/Ecol/Data"

@@

The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh]Sumaila et al., this Special Feature), and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb]. Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries. These countries have a long history of fisheries cooperation participating in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@NOAA:2018tu]. Furthermore, climate-related fluctuations in stocks' distribution have historically created disputes between Canada and the US, increasing international conflict and threatening the health of diverse transboundary stocks [@Munro:2002uf; @CIA:2017uta].

@@

path_world <- "~/Documents/Github/Oceana_LA/international/information/raw_databases/Spatial/TM_WORLD_BORDERS-0.3"
file_name <- "TM_WORLD_BORDERS"

@@

path_eez <- ("/Users/jpalacios/Documents/R CODE/Spatial_Analysis/Data/World_EEZ_v10_2018")
#The File
fnam_eez <- "eez_v10.shp"

@@

path_IPHC <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/IPHC/IPHC_RegulatoryAreas/")

@@

path_NAFO <- ("/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/NAFO")
#The File
fnam_NAFO <- "Divisions"

@@

Path_Save <- "/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/Others/"

ggsave("Fig1_NA.png",
    plot = North_A,
    width = 6,
    height = 5,
    units = "in",
    path = Path_Save)

@@

# Save plot for manuscrip
ggsave("Fig1_NAFO.png",
    plot = NAFO,
    width = 6,
    height = 5,
    units = "in",
    path = Path_Save)

@@

# Save plot for manuscrip
ggsave("Fig1_IPHC.png",
    plot = IPHC,
    width = 6,
    height = 5,
    units = "in",
    path = Path_Save)

@@

# List of DBEM INDEX within the EEZ
#Data provided by Vicki Lam
EEZIDs_List <- read_excel(paste(Data_Path,"/Spatial/Updated_EEZList_17June2016.xlsx",sep=""))
EEZ_CellID <- read_excel(paste(Data_Path,"/Spatial/EEZ_CellID.xlsx",sep=""))
colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread(paste(Data_Path,"/Spatial/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

@@

path_world <- paste(Data_Path,"/Spatial/TM_WORLD_BORDERS",sep="")
file_name <- "TM_WORLD_BORDERS"

@@

path_eez <- paste(Data_Path,"/Spatial/World_EEZ_v10_2018",sep="")
#The File
fnam_eez <- "eez_v10.shp"

@@

# Now we load IPHC shapefiles ####
path_IPHC <- paste(Data_Path,"/Spatial/IPHC_RegulatoryAreas/",sep="")

@@

# Species data (Names, treaties, etc)
# DBEM exploited species list 
exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")

# IPHC and GB species
Selected_Species <- fread("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/List_Species.csv")

# NAFO Species
# This is the subset of species Fished on canada and US waters of all NAFO's species list
NAFO_Species <- read.csv("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/NAFO_Species.csv") %>%
 mutate(Treaty = "NAFO")

@@

@@

# List of DBEM INDEX within the EEZ
#Data provided by Vicki Lam
EEZIDs_List <- read_excel(paste(Data_Path,"/Spatial/Updated_EEZList_17June2016.xlsx",sep=""))
EEZ_CellID <- read_excel(paste(Data_Path,"/Spatial/EEZ_CellID.xlsx",sep=""))
colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread(paste(Data_Path,"/Spatial/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

# From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
Raw_DBEM_Results <- data.table::fread(paste(Data_Path,"/Distribution/Raw_Data.csv",sep="")) %>% 
 filter(Species != "Anoplopoma fimbria") #Remove

@@

# Path to save the plots
Path <- "./Results/North_America"
RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP

@@

# Path to save the plots
Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results/North_America"
RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP

@@

#For paper (Table 2)
write.csv(SS_Change,
     "./Ecology/Results/North_America/SS_Change.csv",
     row.names = F)

@@

# Path for saving plots
Path <- "./Results/IPHC"
RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
#### New version

@@

img <- readPNG("/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/Fig3.png")
grid.raster(img)

@@

# Set saving path
Path <- "./Manuscript/Results/IPHC/Proportion"

IPHC_Species <- c("Hippoglossus stenolepis") # Halibut

@@

Fig4 <- readPNG("~/Documents/UBC/Oceans_Project/Manuscript/Results/Fig4.png")
grid.raster(Fig4)

@@

# Path for saving plots
Path <- "./Results/GoM/"

@@

### Analysis by Species ####

Path <- "~/Documents/UBC/Oceans_Project/Manuscript/Results"
# names(DBEM_Results)

@@

![Fig 6.Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present. Values represent the mean of 3 ESM; error bars represent $\mp$ sd. (2005-2014).](./Figures/Fig6.png)

@@

# Read Data
Environmental_Data_Halibut <- read.csv("~/Documents/UBC/OC_Special_Issue/Ecol/Data/Distribution/Environmental_Data_Halibut.csv")

>>>>

@@

# End Century
End_In <- paste(2080);End_In # 2090
End_End <- paste(2099);End_End
```

@@

The shifts in distribution of shared fish stocks will impact the economics of their fisheries [@Pinsky:2012kq; @Sumaila:2019gh]Sumaila et al., this Special Feature), and create international disputes between countries [@Munro:2002uf; @Spijkers:2017ij; @Pinsky:2018cb]. Canada and the US share important transboundary stocks of salmon (*Oncorhynchus spp.*), Pacific halibut (*Hippoglossus stenolepis*), and Atlantic cod (*Gadus morhua*) offering a unique lens to understand the extent to which climate-induced distributional shifts will challenge the future sustainability of transboundary fisheries. These countries have a long history of fisheries cooperation participating in diverse, jointly managed, commercial transboundary stocks through various fisheries management organizations [@NOAA:218tu]. Furthermore, climate-related fluctuations in stocks' distribution have historically created disputes between Canada and the US, increasing international conflict and threatening the health of diverse transboundary stocks [@Munro:2002uf; @CIA:2017uta].

@@

### North America Initial Map ####
path_world <- my_path("G",Extra_Path = "Spatial/TM_WORLD_BORDERS-0.3")
file_name <- "TM_WORLD_BORDERS"

@@

### North America EEZs Map ####
path_eez <- my_path("G",Extra_Path = "Spatial/World_EEZ_v10_2018-0.3")
#The File
fnam_eez <- "eez_v10.shp"

@@

path_IPHC <- my_path("D",Extra_Path = "IPHC/IPHC_RegulatoryAreas/")

@@

path_NAFO <- paste(Data_path,"Spatial/NAFO")
#The File
fnam_NAFO <- "Divisions"

@@

ggsave("Fig1_NA.png",
    plot = North_A,
    width = 6,
    height = 5,
    units = "in",
    path = Results_Path)

@@

# Save plot for manuscrip
ggsave("Fig1_NAFO.png",
    plot = NAFO,
    width = 6,
    height = 5,
    units = "in",
    path = my_path("R"))

@@

# Save plot for manuscrip
ggsave("Fig1_IPHC.png",
    plot = IPHC,
    width = 6,
    height = 5,
    units = "in",
    path = my_path("R"))

@@

# List of DBEM INDEX within the EEZ
#Data provided by Vicki Lam
EEZIDs_List <- my_path("G",Extra_Path = "Spatial/DBEM",Name="Updated_EEZList_17June2016.xlsx",Read = TRUE)

EEZ_CellID <- my_path("G",Extra_Path = "Spatial/DBEM",Name="EEZ_CellID.xlsx",Read = TRUE)
colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- my_path("G",Extra_Path = "Spatial/DBEM", Name = "Lon_Lat_DBEM.txt", Read = TRUE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

@@

path_world <- my_path("D",Extra_Path = "Spatial/TM_WORLD_BORDERS")
file_name <- "TM_WORLD_BORDERS"

@@

path_eez <- my_path("D",Extra_Path = "Spatial/World_EEZ_v10_2018")
#The File
fnam_eez <- "eez_v10.shp"

@@

# Now we load IPHC shapefiles ####
path_IPHC <- my_path("D",Extra_Path = "Spatial/IPHC_RegulatoryAreas")
# The Canada file
fnam_IPHC_C <- "IPHC_RegulatoryAreas_CAN"

@@

# Species data (Names, treaties, etc)
# DBEM exploited species list (ONLY ON DROBO)
exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")

# IPHC and GB species
Selected_Species <- fread(paste(Data_Path,"Species/List_Species.csv",sep=""))

# NAFO Species
# This is the subset of species Fished on canada and US waters of all NAFO's species list
NAFO_Species <- read.csv(paste(Data_Path,"Species/NAFO_Species.csv",sep="")) %>%
 mutate(Treaty = "NAFO")

@@

#-------------------- NOTE --------------------#
# Chunk to be ran in Hall100 connected to DROBO
#---------------------------------------------#

@@

# List of DBEM INDEX within the EEZ
#Data provided by Vicki Lam
EEZIDs_List <- read_excel(paste(my_path("G",Extra_Path = "Spatial/DBEM"),"Updated_EEZList_17June2016.xlsx",sep=""))

x <- paste(my_path("G",Extra_Path = "Spatial/DBEM"),"Updated_EEZList_17June2016.xlsx",sep="")

str_detect(x,".xlsx")

EEZ_CellID <- read_excel(paste(my_path("G",Extra_Path = "Spatial/DBEM"),"EEZ_CellID.xlsx",sep=""))
colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- my_path("G",Extra_Path = "Spatial/DBEM", Name = "Lon_Lat_DBEM.txt", Read = TRUE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

# Raw DBEM results
Raw_DBEM_Results <- my_path("D",Extra_Path = "Ecol/Distribution", Name = "Raw_Data.csv", Read = TRUE)

%>% 
 filter(Species != "Anoplopoma fimbria") #Remove

@@

# Path to save the plots
Path <- my_path("R",Extra_Path = "North_America")
RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP

@@

# Path to save the plots
Path <- my_path("R",Extra_Path = "North_America")
RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP

@@

Path <- my_path("R",Extra_Path = "North_America")

#For paper (Table 2)
write.csv(SS_Change,
     paste(Path,"SS_Change.csv",sep=""),
     row.names = F)

@@

# Path for saving plots
Path <- my_path("R",Extra_Path = "IPHC")
RCP = c("GFDL26F1","IPSL26F1","MPI26F1") #Low RCP
#### New version

@@

img <- readPNG(paste(my_path("F"),"Figure 3.png",sep=""))
grid.raster(img)

@@

# Set saving path
Path <- my_path("R",Extra_Path = "IPHC/Proportion")
IPHC_Species <- c("Hippoglossus stenolepis") # Halibut

@@

Fig4 <- readPNG(paste(my_path("F"),"Figure 4.png",sep=""))
grid.raster(Fig4)

@@

# Path for saving plots
Path <- my_path("R",Extra_Path = "GoM")

@@

### Analysis by Species ####
Path <- my_path("R", Extra_Path = "GoM")

# names(DBEM_Results)

@@

![Fig 6.Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present. Values represent the mean of 3 ESM; error bars represent $\mp$ sd. (2005-2014).](./Figures/Figure 6.png)

@@

# Read Data
Environmental_Data_Halibut <- read.csv(paste(my_path("D","Distribution"),"Environmental_Data_Halibut.csv",sep=""))
